Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-20 GEMDataSource.Rmd
Minor edits
Found appropriate range for Sim
minor

* repmis  
* tidyr  
* reshape  
* plyr  
* WDI

@@

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, PercentPerceived = 20:100)

@@

# Plot simulation
plot(simz2)

>>>>

- repmis  
- tidyr  
- reshape  
- plyr  
- WDI

@@

# Find appropriate range for PercentPerceived
summary(CompleteData_omit$PercentPerceived)

# Set range of PercentPerceived values in simulation
x.out2 <- setx(Z1, PercentPerceived = 9:67)

@@

# Plot simulation
plot(simz2, xlab= 'PercentPerceived')
